Carbonate chemistry at Ny-Ålesund

### 2022-03-30 awipev-CO2.Rmd
figs air-sea CO2

![](Images/AWIPEV-Logo.jpg){width="250px"}

@@

::: {style="text-align:center" markdown="1"}
<img src="./Images/Container.png" width="200" height="200"/>
<img src="./Images/Intake.png" width="200" height="200"/>
<img src="./Images/2018-04-17_Ferrybox2.jpg" width="200" height="200"/>
:::

@@

p_f_air_sea <- ggplot(data = d_all) +
  geom_point(aes(x = datetime, y = f_air_sea), col = "blue", size = 0.15, na.rm = TRUE) +
  labs(title = "Air-sea CO2 flux (all data)", x = "Time", y = "CO2 (mmol/(m2 h))") +
  Mytheme(size_labs = 8)
#p_f_air_sea
#ggsave(filename = "figures/f_air_sea.png", plot = f_air_sea, width = 20, units = "cm")

@@

p_f_air_sea_d <- ggplot(data = air_sea_day) +
  geom_point(aes(x = day, y = f_air_sea), col = "blue", size = 0.15, na.rm = TRUE) +
  labs(title = "Air-sea CO2 flux (per day)", x = "Julian day", y = "CO2 (mmol/(m2 d))") +
  Mytheme(size_labs = 8)
#p_f_air_sea_d
#ggsave(filename = "figures/f_air_sea_d.png", plot = p_f_air_sea_d, width = 20, units = "cm")

air_sea_month <- d_all %>%
  dplyr::select(monthd, f_air_sea) %>%
  dplyr::group_by(monthd) %>%
  dplyr::summarise(f_air_sea = 24 * mean(f_air_sea, na.rm = TRUE)/1000) %>% #mol/(m2 d)
  ungroup() %>%
  dplyr::mutate(f_air_sea = days_in_month(monthd) * f_air_sea) %>% 
  dplyr::mutate(montht = month(monthd, label = TRUE, abbr = TRUE))
#air_sea_month
p_f_air_sea_m <- ggplot(data = air_sea_month) +
  geom_point(aes(x = montht, y = f_air_sea), col = "blue", size = 2, na.rm = TRUE) +
  #scale_x_discrete(breaks=c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", "")) +
  #lims(y = c(-30, 0)) +
  labs(title = "Air-sea CO2 flux (per month)", x = "Month", y = "CO2 (mmol/(m2 month))") +
  Mytheme(size_labs = 8)
#p_f_air_sea_m
#ggsave(filename = "figures/f_air_sea_m.png", plot = p_f_air_sea_m, width = 20, units = "cm")

@@

::: {style="text-align:center" markdown="1"}
<img src="./Images/2016-04-04_leakage_AT_analyser1.jpg" width="200" height="200"/>
<img src="./Images/2016-04-04_leakage_AT_analyser3.jpg" width="200" height="200"/>
:::

@@

![](Images/awipev_server_arborescence.jpg){width="65%"}

>>>>

![](images/AWIPEV-Logo.jpg){width="250px"}

@@

::: {style="text-align:center" markdown="1"}
<img src="./images/Container.png" width="200" height="200"/>
<img src="./images/Intake.png" width="200" height="200"/>
<img src="./images/2018-04-17_Ferrybox2.jpg" width="200" height="200"/>
:::

@@

p_f_air_sea <- ggplot(data = d_all) +
  geom_point(aes(x = datetime, y = f_air_sea), col = "blue", size = 0.15, na.rm = TRUE) +
  labs(title = "Air-sea CO2 flux (all data)", x = "Time", y = "CO2 (mmol/(m2 h))") +
  Mytheme(size_labs = 8)
p_f_air_sea
ggsave(filename = "figures/f_air_sea.png", plot = f_air_sea, width = 20, units = "cm")

@@

p_f_air_sea_d <- ggplot(data = air_sea_day) +
  geom_point(aes(x = day, y = f_air_sea), col = "blue", size = 0.15, na.rm = TRUE) +
  labs(title = "Air-sea CO2 flux (per day)", x = "Julian day", y = "CO2 (mmol/(m2 d))") +
  Mytheme(size_labs = 8)
p_f_air_sea_d
ggsave(filename = "figures/f_air_sea_d.png", plot = p_f_air_sea_d, width = 20, units = "cm")

air_sea_month <- d_all %>%
  dplyr::select(monthd, f_air_sea) %>%
  dplyr::group_by(monthd) %>%
  dplyr::summarise(f_air_sea = 24 * mean(f_air_sea, na.rm = TRUE)/1000) %>% #mol/(m2 d)
  ungroup() %>%
  dplyr::mutate(f_air_sea = days_in_month(monthd) * f_air_sea) %>% 
  dplyr::mutate(montht = month(monthd, label = TRUE, abbr = TRUE))
#air_sea_month
p_f_air_sea_m <- ggplot(data = air_sea_month) +
  geom_point(aes(x = montht, y = f_air_sea), col = "blue", size = 2, na.rm = TRUE) +
  #scale_x_discrete(breaks=c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", "")) +
  #lims(y = c(-30, 0)) +
  labs(title = "Air-sea CO2 flux (per month)", x = "Month", y = "CO2 (mmol/(m2 month))") +
  Mytheme(size_labs = 8)
p_f_air_sea_m
ggsave(filename = "figures/f_air_sea_m.png", plot = p_f_air_sea_m, width = 20, units = "cm")

@@

::: {style="text-align:center" markdown="1"}
<img src="./images/2016-04-04_leakage_AT_analyser1.jpg" width="200" height="200"/>
<img src="./images/2016-04-04_leakage_AT_analyser3.jpg" width="200" height="200"/>
:::

@@

![](images/awipev_server_arborescence.jpg){width="65%"}
